### 2014-09-25 LaTeX/mCapSimPlot.tex
updates to tex, and plots

% Created by tikzDevice version 0.7.0 on 2014-09-23 11:40:21
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (433.62,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 39.69, 34.03) rectangle (421.57,277.03);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[fill=fillColor] ( 39.69, 34.03) rectangle (421.57,277.03);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 57.05,107.99) --
	( 61.80,109.63) --
	( 66.56,111.28) --
	( 71.31,112.93) --
	( 76.07,114.58) --
	( 80.82,116.22) --
	( 85.58,117.87) --
	( 90.34,119.52) --
	( 95.09,121.16) --
	( 99.85,122.81) --
	(104.60,124.46) --
	(109.36,126.11) --
	(114.11,127.75) --
	(118.87,129.40) --
	(123.63,131.05) --
	(128.38,132.70) --
	(133.14,134.34) --
	(137.89,135.99) --
	(142.65,137.64) --
	(147.40,139.28) --
	(152.16,140.93) --
	(156.92,142.58) --
	(161.67,144.23) --
	(166.43,145.87) --
	(171.18,147.52) --
	(175.94,149.17) --
	(180.70,150.81) --
	(185.45,152.46) --
	(190.21,154.11) --
	(194.96,155.76) --
	(199.72,157.40) --
	(204.47,159.05) --
	(209.23,160.70) --
	(213.99,162.34) --
	(218.74,163.99) --
	(223.50,165.64) --
	(228.25,167.29) --
	(233.01,168.93) --
	(237.76,170.58) --
	(242.52,172.23) --
	(247.28,173.88) --
	(252.03,175.52) --
	(256.79,177.17) --
	(261.54,178.82) --
	(266.30,180.46) --
	(271.05,182.11) --
	(275.81,183.76) --
	(280.57,185.41) --
	(285.32,187.05) --
	(290.08,188.70) --
	(294.83,190.35) --
	(299.59,191.99) --
	(304.35,193.64) --
	(309.10,195.29) --
	(313.86,196.94) --
	(318.61,198.58) --
	(323.37,200.23) --
	(328.12,201.88) --
	(332.88,203.52) --
	(337.64,205.17) --
	(342.39,206.82) --
	(347.15,208.47) --
	(351.90,210.11) --
	(356.66,211.76) --
	(361.41,213.41) --
	(366.17,215.05) --
	(370.93,216.70) --
	(375.68,218.35) --
	(380.44,220.00) --
	(385.19,221.64) --
	(389.95,223.29) --
	(394.70,224.94) --
	(399.46,226.59) --
	(404.22,228.23);
\definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}

\path[fill=fillColor,fill opacity=0.30] ( 57.05,170.30) --
	( 61.80,170.75) --
	( 66.56,171.43) --
	( 71.31,172.00) --
	( 76.07,172.73) --
	( 80.82,173.39) --
	( 85.58,174.13) --
	( 90.34,174.65) --
	( 95.09,175.20) --
	( 99.85,175.83) --
	(104.60,176.50) --
	(109.36,177.16) --
	(114.11,177.80) --
	(118.87,178.59) --
	(123.63,179.29) --
	(128.38,179.81) --
	(133.14,180.41) --
	(137.89,181.20) --
	(142.65,181.89) --
	(147.40,182.78) --
	(152.16,183.41) --
	(156.92,183.93) --
	(161.67,184.69) --
	(166.43,185.42) --
	(171.18,186.20) --
	(175.94,187.05) --
	(180.70,188.02) --
	(185.45,188.60) --
	(190.21,189.50) --
	(194.96,190.46) --
	(199.72,191.24) --
	(204.47,192.15) --
	(209.23,193.07) --
	(213.99,194.11) --
	(218.74,195.08) --
	(223.50,196.00) --
	(228.25,196.95) --
	(233.01,198.08) --
	(237.76,199.37) --
	(242.52,200.49) --
	(247.28,201.79) --
	(252.03,203.07) --
	(256.79,204.30) --
	(261.54,205.54) --
	(266.30,207.04) --
	(271.05,208.33) --
	(275.81,209.80) --
	(280.57,211.29) --
	(285.32,212.83) --
	(290.08,214.53) --
	(294.83,216.23) --
	(299.59,217.85) --
	(304.35,219.60) --
	(309.10,221.58) --
	(313.86,223.41) --
	(318.61,225.32) --
	(323.37,227.31) --
	(328.12,229.50) --
	(332.88,231.70) --
	(337.64,233.85) --
	(342.39,235.89) --
	(347.15,238.03) --
	(351.90,240.17) --
	(356.66,242.38) --
	(361.41,244.58) --
	(366.17,246.95) --
	(370.93,249.06) --
	(375.68,251.34) --
	(380.44,253.72) --
	(385.19,255.97) --
	(389.95,258.60) --
	(394.70,261.10) --
	(399.46,263.65) --
	(404.22,265.99) --
	(404.22,189.23) --
	(399.46,188.51) --
	(394.70,187.90) --
	(389.95,187.02) --
	(385.19,186.13) --
	(380.44,185.09) --
	(375.68,184.39) --
	(370.93,183.61) --
	(366.17,182.69) --
	(361.41,181.83) --
	(356.66,180.81) --
	(351.90,179.77) --
	(347.15,178.57) --
	(342.39,177.44) --
	(337.64,176.32) --
	(332.88,175.29) --
	(328.12,174.08) --
	(323.37,172.90) --
	(318.61,171.57) --
	(313.86,170.24) --
	(309.10,168.76) --
	(304.35,167.31) --
	(299.59,165.82) --
	(294.83,164.52) --
	(290.08,162.91) --
	(285.32,161.16) --
	(280.57,159.46) --
	(275.81,157.79) --
	(271.05,155.95) --
	(266.30,154.07) --
	(261.54,152.24) --
	(256.79,150.23) --
	(252.03,148.25) --
	(247.28,146.22) --
	(242.52,143.99) --
	(237.76,141.83) --
	(233.01,139.84) --
	(228.25,137.63) --
	(223.50,135.49) --
	(218.74,133.10) --
	(213.99,130.62) --
	(209.23,128.31) --
	(204.47,125.87) --
	(199.72,123.59) --
	(194.96,121.22) --
	(190.21,118.75) --
	(185.45,116.43) --
	(180.70,114.03) --
	(175.94,111.47) --
	(171.18,108.99) --
	(166.43,106.38) --
	(161.67,103.74) --
	(156.92,101.22) --
	(152.16, 98.74) --
	(147.40, 96.24) --
	(142.65, 93.73) --
	(137.89, 91.21) --
	(133.14, 88.50) --
	(128.38, 85.77) --
	(123.63, 83.16) --
	(118.87, 80.48) --
	(114.11, 77.79) --
	(109.36, 75.08) --
	(104.60, 72.30) --
	( 99.85, 69.52) --
	( 95.09, 66.86) --
	( 90.34, 64.14) --
	( 85.58, 61.43) --
	( 80.82, 58.71) --
	( 76.07, 55.94) --
	( 71.31, 53.21) --
	( 66.56, 50.50) --
	( 61.80, 47.80) --
	( 57.05, 45.08) --
	cycle;
\definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}

\path[fill=fillColor,fill opacity=0.50] ( 57.05,159.56) --
	( 61.80,160.25) --
	( 66.56,160.98) --
	( 71.31,161.86) --
	( 76.07,162.52) --
	( 80.82,163.37) --
	( 85.58,164.21) --
	( 90.34,164.90) --
	( 95.09,165.74) --
	( 99.85,166.75) --
	(104.60,167.59) --
	(109.36,168.46) --
	(114.11,169.19) --
	(118.87,170.16) --
	(123.63,170.99) --
	(128.38,171.84) --
	(133.14,172.69) --
	(137.89,173.59) --
	(142.65,174.41) --
	(147.40,175.17) --
	(152.16,176.19) --
	(156.92,177.17) --
	(161.67,178.09) --
	(166.43,178.94) --
	(171.18,179.97) --
	(175.94,180.98) --
	(180.70,181.99) --
	(185.45,182.96) --
	(190.21,183.82) --
	(194.96,184.88) --
	(199.72,185.88) --
	(204.47,186.83) --
	(209.23,187.76) --
	(213.99,188.99) --
	(218.74,190.13) --
	(223.50,191.26) --
	(228.25,192.31) --
	(233.01,193.53) --
	(237.76,194.62) --
	(242.52,195.84) --
	(247.28,197.18) --
	(252.03,198.48) --
	(256.79,199.68) --
	(261.54,201.07) --
	(266.30,202.56) --
	(271.05,204.06) --
	(275.81,205.62) --
	(280.57,207.24) --
	(285.32,209.00) --
	(290.08,210.51) --
	(294.83,212.14) --
	(299.59,213.87) --
	(304.35,215.72) --
	(309.10,217.52) --
	(313.86,219.34) --
	(318.61,221.26) --
	(323.37,223.16) --
	(328.12,225.10) --
	(332.88,227.06) --
	(337.64,228.96) --
	(342.39,231.01) --
	(347.15,233.07) --
	(351.90,235.12) --
	(356.66,237.31) --
	(361.41,239.43) --
	(366.17,241.62) --
	(370.93,243.83) --
	(375.68,246.04) --
	(380.44,248.34) --
	(385.19,250.61) --
	(389.95,252.92) --
	(394.70,255.34) --
	(399.46,257.65) --
	(404.22,260.08) --
	(404.22,196.18) --
	(399.46,195.16) --
	(394.70,194.11) --
	(389.95,193.22) --
	(385.19,192.29) --
	(380.44,191.22) --
	(375.68,190.29) --
	(370.93,189.27) --
	(366.17,188.31) --
	(361.41,187.21) --
	(356.66,185.94) --
	(351.90,184.86) --
	(347.15,183.77) --
	(342.39,182.69) --
	(337.64,181.59) --
	(332.88,180.34) --
	(328.12,179.09) --
	(323.37,177.75) --
	(318.61,176.29) --
	(313.86,174.79) --
	(309.10,173.33) --
	(304.35,171.86) --
	(299.59,170.35) --
	(294.83,168.77) --
	(290.08,167.23) --
	(285.32,165.59) --
	(280.57,163.88) --
	(275.81,162.14) --
	(271.05,160.29) --
	(266.30,158.47) --
	(261.54,156.48) --
	(256.79,154.63) --
	(252.03,152.76) --
	(247.28,150.64) --
	(242.52,148.69) --
	(237.76,146.57) --
	(233.01,144.54) --
	(228.25,142.40) --
	(223.50,140.17) --
	(218.74,137.98) --
	(213.99,135.99) --
	(209.23,133.82) --
	(204.47,131.54) --
	(199.72,129.37) --
	(194.96,127.03) --
	(190.21,124.77) --
	(185.45,122.49) --
	(180.70,120.16) --
	(175.94,117.80) --
	(171.18,115.40) --
	(166.43,113.13) --
	(161.67,110.68) --
	(156.92,108.42) --
	(152.16,105.89) --
	(147.40,103.39) --
	(142.65,100.83) --
	(137.89, 98.32) --
	(133.14, 95.77) --
	(128.38, 93.33) --
	(123.63, 90.81) --
	(118.87, 88.34) --
	(114.11, 85.90) --
	(109.36, 83.33) --
	(104.60, 80.84) --
	( 99.85, 78.40) --
	( 95.09, 75.83) --
	( 90.34, 73.27) --
	( 85.58, 70.75) --
	( 80.82, 68.24) --
	( 76.07, 65.78) --
	( 71.31, 63.28) --
	( 66.56, 60.67) --
	( 61.80, 58.16) --
	( 57.05, 55.65) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.69, 34.03) --
	( 39.69,277.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,101.49) {3.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,183.81) {4.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,266.13) {4.2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.69, 34.03) --
	(421.57, 34.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 41.46, 20.31) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 89.02, 20.31) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (136.58, 20.31) {2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (184.13, 20.31) {3};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (231.69, 20.31) {4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (279.25, 20.31) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (326.81, 20.31) {6};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (374.36, 20.31) {7};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (230.63,  4.82) {Ln(Min. Cap Dist.)$_{t}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

>>>>

% Created by tikzDevice version 0.7.0 on 2014-09-25 14:22:37
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (433.62,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 52.48, 34.03) rectangle (421.57,277.03);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[fill=fillColor] ( 52.48, 34.03) rectangle (421.57,277.03);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 69.26,107.02) --
	( 76.56,109.63) --
	( 80.61,111.07) --
	( 80.74,111.12) --
	( 93.47,115.66) --
	(101.51,118.53) --
	(106.88,120.45) --
	(109.99,121.56) --
	(116.04,123.72) --
	(124.61,126.77) --
	(153.74,137.17) --
	(166.44,141.70) --
	(169.66,142.85) --
	(182.48,147.43) --
	(189.23,149.83) --
	(198.25,153.05) --
	(202.82,154.68) --
	(205.60,155.68) --
	(205.69,155.71) --
	(206.30,155.92) --
	(207.92,156.50) --
	(209.67,157.13) --
	(214.56,158.87) --
	(214.75,158.94) --
	(219.02,160.46) --
	(220.78,161.09) --
	(224.96,162.59) --
	(226.35,163.08) --
	(226.45,163.12) --
	(226.69,163.20) --
	(227.16,163.37) --
	(229.07,164.05) --
	(229.22,164.10) --
	(229.80,164.31) --
	(230.46,164.55) --
	(231.37,164.87) --
	(232.05,165.12) --
	(232.29,165.20) --
	(232.34,165.22) --
	(232.73,165.36) --
	(237.64,167.11) --
	(239.57,167.80) --
	(239.75,167.86) --
	(240.75,168.22) --
	(241.66,168.54) --
	(242.52,168.85) --
	(243.48,169.19) --
	(244.41,169.52) --
	(245.54,169.93) --
	(245.55,169.93) --
	(247.34,170.57) --
	(247.36,170.58) --
	(248.05,170.82) --
	(248.78,171.09) --
	(249.23,171.25) --
	(249.60,171.38) --
	(252.59,172.45) --
	(255.95,173.64) --
	(257.34,174.14) --
	(257.79,174.30) --
	(257.94,174.35) --
	(258.24,174.46) --
	(259.46,174.90) --
	(259.93,175.06) --
	(261.11,175.48) --
	(261.30,175.55) --
	(261.73,175.70) --
	(263.06,176.18) --
	(264.22,176.59) --
	(266.18,177.29) --
	(267.22,177.66) --
	(267.29,177.69) --
	(268.47,178.11) --
	(269.59,178.51) --
	(270.46,178.82) --
	(271.09,179.05) --
	(271.37,179.15) --
	(271.86,179.32) --
	(271.89,179.33) --
	(272.02,179.38) --
	(272.38,179.51) --
	(272.44,179.53) --
	(273.54,179.92) --
	(273.54,179.92) --
	(274.54,180.28) --
	(274.62,180.31) --
	(274.74,180.35) --
	(274.93,180.42) --
	(275.09,180.47) --
	(275.27,180.54) --
	(275.51,180.62) --
	(275.85,180.75) --
	(276.03,180.81) --
	(276.19,180.86) --
	(276.46,180.96) --
	(276.61,181.01) --
	(278.14,181.56) --
	(278.91,181.83) --
	(278.99,181.86) --
	(279.48,182.04) --
	(279.57,182.07) --
	(279.84,182.17) --
	(280.03,182.23) --
	(280.82,182.52) --
	(281.34,182.70) --
	(281.36,182.71) --
	(281.96,182.92) --
	(282.46,183.10) --
	(282.56,183.14) --
	(283.13,183.34) --
	(283.17,183.36) --
	(283.65,183.53) --
	(283.74,183.56) --
	(285.14,184.06) --
	(285.23,184.09) --
	(285.29,184.11) --
	(285.32,184.13) --
	(285.65,184.24) --
	(286.10,184.40) --
	(286.16,184.42) --
	(286.46,184.53) --
	(286.60,184.58) --
	(286.65,184.60) --
	(286.71,184.62) --
	(286.73,184.63) --
	(286.83,184.66) --
	(286.86,184.67) --
	(287.36,184.85) --
	(287.70,184.97) --
	(287.78,185.00) --
	(289.22,185.51) --
	(289.39,185.58) --
	(289.45,185.60) --
	(289.83,185.73) --
	(289.89,185.75) --
	(290.32,185.91) --
	(290.49,185.97) --
	(290.52,185.98) --
	(290.79,186.08) --
	(290.84,186.09) --
	(290.85,186.10) --
	(290.85,186.10) --
	(290.88,186.11) --
	(290.92,186.12) --
	(291.46,186.31) --
	(291.68,186.39) --
	(292.03,186.52) --
	(292.66,186.74) --
	(292.90,186.83) --
	(293.68,187.11) --
	(294.05,187.24) --
	(294.33,187.34) --
	(294.72,187.48) --
	(294.89,187.54) --
	(294.98,187.57) --
	(295.14,187.63) --
	(295.44,187.73) --
	(295.54,187.77) --
	(295.80,187.86) --
	(296.23,188.02) --
	(297.04,188.31) --
	(297.20,188.36) --
	(297.32,188.41) --
	(297.39,188.43) --
	(297.92,188.62) --
	(298.07,188.67) --
	(298.46,188.81) --
	(298.47,188.82) --
	(298.54,188.84) --
	(298.62,188.87) --
	(299.15,189.06) --
	(299.26,189.10) --
	(299.54,189.20) --
	(299.58,189.21) --
	(300.71,189.62) --
	(301.41,189.86) --
	(302.13,190.12) --
	(302.61,190.29) --
	(303.45,190.59) --
	(303.55,190.63) --
	(303.59,190.64) --
	(303.66,190.67) --
	(303.89,190.75) --
	(303.92,190.76) --
	(304.13,190.84) --
	(304.31,190.90) --
	(304.32,190.90) --
	(304.63,191.01) --
	(305.44,191.30) --
	(306.03,191.51) --
	(306.65,191.74) --
	(307.10,191.90) --
	(307.15,191.91) --
	(307.34,191.98) --
	(307.36,191.99) --
	(307.48,192.03) --
	(307.57,192.06) --
	(307.71,192.11) --
	(307.78,192.14) --
	(307.86,192.17) --
	(308.14,192.27) --
	(308.17,192.28) --
	(308.40,192.36) --
	(309.29,192.68) --
	(309.65,192.80) --
	(309.66,192.81) --
	(309.77,192.85) --
	(309.85,192.88) --
	(310.26,193.02) --
	(310.42,193.08) --
	(310.88,193.25) --
	(310.97,193.28) --
	(311.25,193.38) --
	(312.09,193.68) --
	(312.22,193.72) --
	(312.41,193.79) --
	(313.42,194.15) --
	(313.62,194.22) --
	(313.78,194.28) --
	(314.05,194.38) --
	(314.50,194.54) --
	(314.58,194.57) --
	(314.67,194.60) --
	(315.27,194.81) --
	(315.36,194.84) --
	(315.70,194.96) --
	(315.87,195.03) --
	(315.98,195.06) --
	(316.35,195.20) --
	(316.56,195.27) --
	(316.72,195.33) --
	(317.21,195.50) --
	(317.49,195.60) --
	(317.56,195.63) --
	(318.84,196.09) --
	(318.87,196.09) --
	(319.28,196.24) --
	(319.56,196.34) --
	(319.75,196.41) --
	(319.97,196.49) --
	(320.23,196.58) --
	(320.29,196.60) --
	(320.33,196.62) --
	(320.94,196.84) --
	(321.01,196.86) --
	(321.22,196.93) --
	(321.25,196.94) --
	(321.36,196.98) --
	(321.75,197.12) --
	(323.15,197.62) --
	(323.66,197.81) --
	(325.17,198.34) --
	(325.77,198.56) --
	(325.89,198.60) --
	(326.94,198.97) --
	(327.01,199.00) --
	(327.29,199.10) --
	(328.29,199.46) --
	(328.36,199.48) --
	(328.82,199.65) --
	(329.10,199.75) --
	(329.71,199.96) --
	(330.08,200.10) --
	(330.10,200.10) --
	(330.14,200.12) --
	(330.37,200.20) --
	(330.66,200.30) --
	(331.19,200.49) --
	(331.66,200.66) --
	(331.92,200.75) --
	(332.49,200.96) --
	(333.01,201.14) --
	(334.21,201.57) --
	(334.41,201.64) --
	(334.89,201.81) --
	(337.42,202.72) --
	(337.45,202.72) --
	(337.58,202.77) --
	(337.70,202.81) --
	(337.71,202.82) --
	(337.80,202.85) --
	(339.18,203.34) --
	(339.28,203.38) --
	(341.35,204.12) --
	(341.75,204.26) --
	(342.17,204.41) --
	(342.48,204.52) --
	(342.53,204.54) --
	(342.69,204.60) --
	(342.85,204.65) --
	(343.03,204.72) --
	(343.17,204.77) --
	(343.37,204.84) --
	(343.45,204.87) --
	(343.75,204.97) --
	(343.88,205.02) --
	(344.23,205.14) --
	(345.06,205.44) --
	(346.03,205.79) --
	(346.49,205.95) --
	(347.23,206.21) --
	(347.38,206.27) --
	(348.49,206.66) --
	(348.58,206.70) --
	(349.13,206.89) --
	(349.81,207.14) --
	(350.10,207.24) --
	(350.24,207.29) --
	(350.58,207.41) --
	(351.85,207.86) --
	(352.05,207.94) --
	(352.77,208.19) --
	(353.17,208.34) --
	(353.42,208.43) --
	(353.71,208.53) --
	(354.71,208.88) --
	(355.56,209.19) --
	(357.56,209.90) --
	(357.72,209.96) --
	(357.97,210.05) --
	(358.00,210.06) --
	(358.30,210.17) --
	(358.37,210.19) --
	(358.57,210.26) --
	(358.60,210.27) --
	(358.96,210.40) --
	(358.97,210.41) --
	(359.44,210.57) --
	(359.71,210.67) --
	(359.84,210.72) --
	(359.89,210.73) --
	(359.95,210.75) --
	(360.12,210.82) --
	(360.50,210.95) --
	(360.53,210.96) --
	(361.15,211.18) --
	(361.24,211.21) --
	(361.57,211.33) --
	(362.32,211.60) --
	(362.86,211.79) --
	(362.88,211.80) --
	(362.99,211.84) --
	(363.37,211.98) --
	(365.15,212.61) --
	(365.51,212.74) --
	(365.58,212.76) --
	(365.58,212.76) --
	(366.24,213.00) --
	(366.27,213.01) --
	(366.79,213.19) --
	(367.09,213.30) --
	(367.28,213.37) --
	(367.50,213.45) --
	(367.74,213.54) --
	(368.30,213.73) --
	(368.30,213.73) --
	(368.38,213.76) --
	(368.49,213.80) --
	(368.90,213.95) --
	(369.46,214.15) --
	(370.56,214.54) --
	(370.74,214.60) --
	(370.85,214.64) --
	(372.47,215.22) --
	(373.39,215.55) --
	(373.79,215.69) --
	(374.21,215.84) --
	(375.70,216.37) --
	(378.93,217.53) --
	(380.42,218.06) --
	(385.52,219.88) --
	(386.08,220.08) --
	(386.54,220.24) --
	(386.90,220.37) --
	(387.31,220.52) --
	(387.53,220.60) --
	(388.24,220.85) --
	(388.35,220.89) --
	(388.69,221.01) --
	(388.71,221.02) --
	(388.75,221.03) --
	(388.90,221.08) --
	(389.17,221.18) --
	(389.73,221.38) --
	(390.59,221.69) --
	(391.22,221.91) --
	(391.77,222.11) --
	(391.82,222.13) --
	(392.15,222.25) --
	(392.41,222.34) --
	(396.33,223.74) --
	(397.13,224.02) --
	(397.28,224.07) --
	(404.32,226.59) --
	(404.80,226.76);
\definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}

\path[fill=fillColor,fill opacity=0.30] ( 69.26,167.58) --
	( 76.56,168.49) --
	( 80.61,169.02) --
	( 80.74,169.02) --
	( 93.47,170.57) --
	(101.51,171.61) --
	(106.88,172.38) --
	(109.99,172.78) --
	(116.04,173.71) --
	(124.61,175.00) --
	(153.74,179.40) --
	(166.44,181.37) --
	(169.66,181.90) --
	(182.48,184.32) --
	(189.23,185.73) --
	(198.25,187.43) --
	(202.82,188.36) --
	(205.60,189.03) --
	(205.69,189.04) --
	(206.30,189.17) --
	(207.92,189.53) --
	(209.67,189.86) --
	(214.56,191.01) --
	(214.75,191.06) --
	(219.02,191.93) --
	(220.78,192.25) --
	(224.96,193.40) --
	(226.35,193.80) --
	(226.45,193.83) --
	(226.69,193.88) --
	(227.16,193.97) --
	(229.07,194.38) --
	(229.22,194.47) --
	(229.80,194.62) --
	(230.46,194.79) --
	(231.37,195.05) --
	(232.05,195.24) --
	(232.29,195.30) --
	(232.34,195.31) --
	(232.73,195.42) --
	(237.64,196.73) --
	(239.57,197.26) --
	(239.75,197.33) --
	(240.75,197.60) --
	(241.66,197.84) --
	(242.52,198.05) --
	(243.48,198.31) --
	(244.41,198.51) --
	(245.54,198.84) --
	(245.55,198.85) --
	(247.34,199.26) --
	(247.36,199.27) --
	(248.05,199.47) --
	(248.78,199.61) --
	(249.23,199.75) --
	(249.60,199.85) --
	(252.59,200.68) --
	(255.95,201.50) --
	(257.34,201.84) --
	(257.79,201.94) --
	(257.94,202.01) --
	(258.24,202.10) --
	(259.46,202.47) --
	(259.93,202.59) --
	(261.11,202.97) --
	(261.30,203.05) --
	(261.73,203.20) --
	(263.06,203.72) --
	(264.22,204.06) --
	(266.18,204.56) --
	(267.22,204.89) --
	(267.29,204.91) --
	(268.47,205.25) --
	(269.59,205.73) --
	(270.46,206.09) --
	(271.09,206.28) --
	(271.37,206.36) --
	(271.86,206.51) --
	(271.89,206.52) --
	(272.02,206.57) --
	(272.38,206.68) --
	(272.44,206.71) --
	(273.54,207.03) --
	(273.54,207.03) --
	(274.54,207.35) --
	(274.62,207.37) --
	(274.74,207.40) --
	(274.93,207.48) --
	(275.09,207.54) --
	(275.27,207.59) --
	(275.51,207.69) --
	(275.85,207.76) --
	(276.03,207.79) --
	(276.19,207.84) --
	(276.46,207.94) --
	(276.61,207.99) --
	(278.14,208.40) --
	(278.91,208.64) --
	(278.99,208.66) --
	(279.48,208.87) --
	(279.57,208.92) --
	(279.84,208.96) --
	(280.03,208.99) --
	(280.82,209.17) --
	(281.34,209.31) --
	(281.36,209.32) --
	(281.96,209.48) --
	(282.46,209.66) --
	(282.56,209.69) --
	(283.13,209.95) --
	(283.17,209.97) --
	(283.65,210.14) --
	(283.74,210.15) --
	(285.14,210.63) --
	(285.23,210.67) --
	(285.29,210.69) --
	(285.32,210.71) --
	(285.65,210.81) --
	(286.10,210.98) --
	(286.16,211.01) --
	(286.46,211.13) --
	(286.60,211.18) --
	(286.65,211.20) --
	(286.71,211.21) --
	(286.73,211.21) --
	(286.83,211.23) --
	(286.86,211.24) --
	(287.36,211.42) --
	(287.70,211.53) --
	(287.78,211.57) --
	(289.22,212.06) --
	(289.39,212.10) --
	(289.45,212.13) --
	(289.83,212.25) --
	(289.89,212.27) --
	(290.32,212.44) --
	(290.49,212.49) --
	(290.52,212.50) --
	(290.79,212.58) --
	(290.84,212.60) --
	(290.85,212.60) --
	(290.85,212.60) --
	(290.88,212.61) --
	(290.92,212.62) --
	(291.46,212.83) --
	(291.68,212.92) --
	(292.03,213.07) --
	(292.66,213.31) --
	(292.90,213.41) --
	(293.68,213.72) --
	(294.05,213.86) --
	(294.33,213.95) --
	(294.72,214.08) --
	(294.89,214.17) --
	(294.98,214.23) --
	(295.14,214.31) --
	(295.44,214.42) --
	(295.54,214.45) --
	(295.80,214.55) --
	(296.23,214.74) --
	(297.04,215.07) --
	(297.20,215.13) --
	(297.32,215.18) --
	(297.39,215.20) --
	(297.92,215.38) --
	(298.07,215.42) --
	(298.46,215.59) --
	(298.47,215.59) --
	(298.54,215.62) --
	(298.62,215.65) --
	(299.15,215.80) --
	(299.26,215.83) --
	(299.54,215.92) --
	(299.58,215.93) --
	(300.71,216.45) --
	(301.41,216.73) --
	(302.13,217.04) --
	(302.61,217.20) --
	(303.45,217.53) --
	(303.55,217.56) --
	(303.59,217.58) --
	(303.66,217.61) --
	(303.89,217.71) --
	(303.92,217.72) --
	(304.13,217.80) --
	(304.31,217.89) --
	(304.32,217.89) --
	(304.63,218.07) --
	(305.44,218.39) --
	(306.03,218.64) --
	(306.65,218.85) --
	(307.10,219.05) --
	(307.15,219.08) --
	(307.34,219.17) --
	(307.36,219.18) --
	(307.48,219.22) --
	(307.57,219.26) --
	(307.71,219.29) --
	(307.78,219.32) --
	(307.86,219.33) --
	(308.14,219.41) --
	(308.17,219.43) --
	(308.40,219.53) --
	(309.29,219.89) --
	(309.65,220.03) --
	(309.66,220.04) --
	(309.77,220.06) --
	(309.85,220.08) --
	(310.26,220.25) --
	(310.42,220.31) --
	(310.88,220.51) --
	(310.97,220.54) --
	(311.25,220.65) --
	(312.09,220.89) --
	(312.22,220.94) --
	(312.41,221.03) --
	(313.42,221.40) --
	(313.62,221.47) --
	(313.78,221.52) --
	(314.05,221.67) --
	(314.50,221.90) --
	(314.58,221.94) --
	(314.67,221.97) --
	(315.27,222.21) --
	(315.36,222.23) --
	(315.70,222.38) --
	(315.87,222.44) --
	(315.98,222.48) --
	(316.35,222.60) --
	(316.56,222.70) --
	(316.72,222.78) --
	(317.21,222.97) --
	(317.49,223.13) --
	(317.56,223.16) --
	(318.84,223.77) --
	(318.87,223.77) --
	(319.28,223.88) --
	(319.56,224.01) --
	(319.75,224.09) --
	(319.97,224.18) --
	(320.23,224.27) --
	(320.29,224.29) --
	(320.33,224.31) --
	(320.94,224.63) --
	(321.01,224.66) --
	(321.22,224.74) --
	(321.25,224.75) --
	(321.36,224.78) --
	(321.75,224.91) --
	(323.15,225.56) --
	(323.66,225.78) --
	(325.17,226.53) --
	(325.77,226.82) --
	(325.89,226.87) --
	(326.94,227.29) --
	(327.01,227.33) --
	(327.29,227.43) --
	(328.29,227.87) --
	(328.36,227.90) --
	(328.82,228.09) --
	(329.10,228.24) --
	(329.71,228.50) --
	(330.08,228.68) --
	(330.10,228.68) --
	(330.14,228.70) --
	(330.37,228.80) --
	(330.66,228.94) --
	(331.19,229.21) --
	(331.66,229.41) --
	(331.92,229.55) --
	(332.49,229.78) --
	(333.01,230.05) --
	(334.21,230.64) --
	(334.41,230.77) --
